\documentclass[../draft.tex]{subfiles}
\begin{document}
I will choose BADP1001 and BADP2001 as my elective courses and I will elaborate on the reasons why I chose them, and explain the source and specific content of these two elective courses. In addition, this report will also explain how these two elective courses help the major of computer science, what kind of help they have in my career, and whether I will have more opportunities in the future after choosing these two elective courses.
\subsubsection{area these electives are from}
According to The University of Sydney (2021), the two elective courses BADP1001 and BADP2001 are from the Architecture and Interaction Design field of the University of Sydney. And BADP1001 is the course learned in the second semester of the first year of Bachelor of Architecture and Environments, and BADP2001 is the course learned in the second semester of the second year of this major. In addition, the credits for both courses are 6 points.
\subsubsection{the electives are}
Regarding the specific content of these two courses, according to The University of Sydney (2021), first of all, the overall content of BADP1001 is to explain the way of working in the built environment based on measurement, analysis and modeling. In addition, this course also explained the concept of quantitative skills to students, and explained how to convey the characteristics of buildings and the feelings of people living in these buildings by measuring the ability of several aspects of buildings and the use of some mathematics. Moreover, this course also explores subjective and objective building data and deviations, and analyzes different types of data, visual representation and mathematical modeling. Secondly, about the course of BADP2001, according to The University of Sydney (2021), its content is a general introduction to the basic skills and concepts of algorithm architecture. In addition, this course uses a series of parametric exercises to explain why modeling is understood as architectural design and the conversion of data into specific information for design analysis. Furthermore, students will also learn a variety of calculation design methods to deepen their understanding of architectural calculation principles.
\subsubsection{knowledge and capabilities will be developed by undertaking these electives} 
Regarding the professional knowledge and abilities that these two courses will allow students to develop, first of all, for the BADP1001 course, according to The University of Sydney (2021), it will guide students how to use instruments to measure the space of buildings and many other characteristics of the built environment, and then Use these data to evaluate the relationship between the characteristics of these buildings and other types of built environment observations and the subjective feelings of end users. Moreover, this course will also develop students' understanding of how to identify the limitations and concepts related to different types of data, and specifically clarify their indispensability in the built environment, and effectively communicate the quantification of the built environment in written form And performance, as well as the ability for students to learn how to critically evaluate the empirical research related to the design and operation of the built environment. Furthermore, it also teaches students how to use quantitative analysis to understand the relationship between the dimensions of the built environment and use these relationships to improve the experience and feelings of the occupants. Next is the course BADP2001, which will develop students' ability to determine architectural design logic and express it through parametric modeling techniques, and develop models with different parameters to simulate the changes and relationships between different design variables. Moreover, according to The University of Sydney (2021), this course will allow students to learn how to effectively use quantitative data in parametric design to complete design analysis and data conversion, and use parametric visualization strategies to algorithmically improve design ideas and solve design problems.
\subsubsection{how these electives might complement the knowledge and capabilities developed as part of the relevant major}
Regarding how these two courses can be used as a supplement to enhance the professional knowledge and ability of computer science, first of all, according to Allen Tucker (n.d.), computer science is a study on computers and computing and their theoretical and practical applications. Computer science encompasses the principles of mathematics, engineering, and logic. These include algorithmic formulas, software and hardware development, and artificial intelligence. And apply these to a large number of computer functions. For the course BADP1001, the content learned in this course can effectively help the major of computer science. According to Eike Send (2005), the main reason is that modern science includes theory, construction and empiricism to varying degrees, which of course also includes computer science. And this course can effectively provide critical thinking to assess the ability of empirical research. I think this ability can help students understand the knowledge of computer science. For example, they can use this kind of critical thinking when they are programming to better improve their own code. For BADP2001, architectural algorithm design is a study that combines computational science with architecture, urban planning and engineering, and computer science is most obviously used to develop CAD and BIM programs, which allows architects to use these programs before building construction Digitize it, model and graph it, and this expertise and capabilities are all related to the algorithm architecture. Moreover, this course can also provide the ability to recognize the basic applications of architectural design and express them through modeling techniques. For example, in two seaside skyscrapers in the UK, these buildings were designed using an algorithm that generates the shape of high-rise buildings so that sunlight reflects off the glass walls and reduces the shadows of other buildings. The beach is kept in the sun instead of being obscured by the shadow of the building. In addition, algorithms are universal, they can still rely on the same features that exist, which can also help students understand the algorithm architecture in computer science.
\subsubsection{if the knowledge and capabilities developed by undertaking these electives will assist in your professional career}
Regarding the professional knowledge and abilities of these two courses to help me in my future career, for BADP1001, I think this course can help me better research and interpret information. Because empirical analysis is an indispensable part of scientific methods, according to TechTarget Contributor (2017), it is a common method to study information through the quantitative observation of empirical evidence to obtain possible answers. In addition, in the IT field, empirical thinking exists in market research, software development, data analysis, and project management. In machine learning, empirical data analysis can be used as a data-driven method, which is different from other probability-driven models. Not affected by potentially restrictive initial assumptions. Next, for the course of BADP2001, algorithm design allows the modeling of highly complex geometric shapes, which will be very helpful for me to combine computer science and architectural science in the future. And the algorithm design requires a parametric modeling concept, which means that the design can be manipulated through variable parameters, which allows me to explore a wider range of possibilities easily and quickly in my future career.
\subsubsection{if there are any opportunities resulting from undertaking these electives}
Regarding whether I have more opportunities in the future, after choosing these two courses, I think these two courses can help me refine my future career path. I can combine the computer major with the architectural major to develop into a professional knowledge and ability that understands both computer and architecture. As mentioned above, become a professional computer architect who can use computers to model and draw buildings. At the same time, some of the direct knowledge of these two majors actually has the same characteristics, which can better help me to have a better understanding than normal students when studying these two majors separately.
\end{document}
